---
title: "Untitled"
author: "Carlos Siri"
date: "5/18/2017"
output:
  html_document: default
  pdf_document: default
---


```{r}
library(NLP)
library(tm)
library(RWeka)
library(ggplot2)
library(wordcloud)
library(RColorBrewer)

```

## Peer Review

Instructions

The goal of this project is just to display that you've gotten used to working with the data and that you are on track to create your prediction algorithm. Please submit a report on R Pubs (http://rpubs.com/) that explains your exploratory analysis and your goals for the eventual app and algorithm. This document should be concise and explain only the major features of the data you have identified and briefly summarize your plans for creating the prediction algorithm and Shiny app in a way that would be understandable to a non-data scientist manager. You should make use of tables and plots to illustrate important summaries of the data set. The motivation for this project is to: 1. Demonstrate that you've downloaded the data and have successfully loaded it in.2. Create a basic report of summary statistics about the data sets.3. Report any interesting findings that you amassed so far.4. Get feedback on your plans for creating a prediction algorithm and Shiny app.
Review criterialess 

Does the link lead to an HTML page describing the exploratory analysis of the training data set?

Has the data scientist done basic summaries of the three files? Word counts, line counts and basic data tables?

Has the data scientist made basic plots, such as histograms to illustrate features of the data?

Was the report written in a brief, concise style, in a way that a non-data scientist manager could appreciate?


```{r}
setwd("C:/Users/siricar/Documents/R/Capstone")
blogs <- readLines(con <- file("final/en_US/en_US.blogs.txt"), encoding = "UTF-8", skipNul = TRUE)
close(con)
news <- readLines(con <- file("final/en_US/en_US.news.txt"), encoding = "UTF-8", skipNul = TRUE)
close(con)
twitter <- readLines(con <- file("final/en_US/en_US.twitter.txt"), encoding = "UTF-8", skipNul = TRUE)
close(con)
```
#File Size
```{r}
news.fileSize <- format(file.info("final/en_US/en_US.news.txt")$size/(1024^2),digits = 0)
blogs.fileSize <- format(file.info("final/en_US/en_US.blogs.txt")$size/(1024^2),digits = 0)
twitter.fileSize <- format(file.info("final/en_US/en_US.twitter.txt")$size/(1024^2),digits = 0)
c(blogs.fileSize, news.fileSize, twitter.fileSize)
```

The files are large 200 mgb for news, 196 mgb for blogs and 159 for twitter.

#Line Count
```{r}
lb <- length(blogs)
ln <-length(news)
lt<-length(twitter)

c(lb,ln,lt)
```
The line count is also big. We will need to sample the data

We will proceed by analysing a sample of the data instead

```{r}
# Data will be sampled

set.seed(1000000)
sampleblogs <- sample(blogs, size = length(blogs)*0.05)
samplenews <- sample(news, size = length(news)*0.05)
sampletwitter <- sample(twitter, size = length(twitter)*0.05)
data.sample <- sample(paste(sampleblogs, samplenews, sampletwitter), size = 10000, replace = TRUE)

# Generate corpus and clean the data

data.sample <- iconv(data.sample, 'UTF-8', 'ASCII')
corpus <- Corpus(VectorSource(as.data.frame(data.sample, stringsAsFactors = FALSE))) 
corpus <- tm_map(corpus, tolower)
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, PlainTextDocument)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removeWords, "na")
corpus <- tm_map(corpus, removeWords, "SMART")

term.doc.matrix <- TermDocumentMatrix(corpus)
term.doc.matrix <- as.matrix(term.doc.matrix)
word.freqs <- sort(rowSums(term.doc.matrix), decreasing=TRUE) 
dm <- data.frame(word=names(word.freqs), freq=word.freqs)

wordcloud(dm$word, dm$freq, min.freq= 500, random.order=TRUE, rot.per=.25)
```
The diagram above provides high level summary of the text

```{r Tokens}
#Tokenize Data

unigram <- NGramTokenizer(corpus, Weka_control(min = 1, max = 1))
bigram <- NGramTokenizer(corpus, Weka_control(min = 2, max = 2)) 
trigram <- NGramTokenizer(corpus, Weka_control(min = 3, max = 3)) 
```

#Unigram

```{r Unigram}
unigram.df <- data.frame(table(unigram))
unigram.df <- unigram.df[order(unigram.df$Freq, decreasing = TRUE),]

ggplot(unigram.df[1:25,], aes(x=unigram, y=Freq)) +
  geom_bar(stat="Identity")+
  xlab("Unigrams") + ylab("Frequency")+
  ggtitle("Bigrams") +
  theme(axis.text.x=element_text(angle=45, hjust=1))

```

#Bigram
```{r Bigram}
bigram.df <- data.frame(table(bigram))
bigram.df <- bigram.df[order(bigram.df$Freq, decreasing = TRUE),]

ggplot(bigram.df[1:25,], aes(x=bigram, y=Freq)) +
  geom_bar(stat="Identity")+
  xlab("Bigrams") + ylab("Frequency")+
  ggtitle("Bigrams") +
  theme(axis.text.x=element_text(angle=45, hjust=1))
```

#TriGram

```{r Trigram}
trigram.df <- data.frame(table(trigram))
trigram.df <- trigram.df[order(trigram.df$Freq, decreasing = TRUE),]

ggplot(trigram.df[1:25,], aes(x=trigram, y=Freq)) +
  geom_bar(stat="Identity")+
  xlab("Trigrams") + ylab("Frequency")+
  ggtitle("Most common 25 Trigrams") +
  theme(axis.text.x=element_text(angle=45, hjust=1))

trigram.df

```


Clean up provided query (the same way corpora has been cleaned up).
Tokenize and compute number of words.
Choose n (for n-gram) equals to number of words plus one word.
Search for appropriate n-grams and order results from common (high frequency, or high probability) to rare.
If nothing found (or less than some coefficient), remove first word from query, and go to the step 3.
Last words of found n-grams represent the prediciton result.
```{r}

txt6
data.sample <- iconv(txt6, 'UTF-8', 'ASCII')
corpus <- Corpus(VectorSource(as.data.frame(data.sample, stringsAsFactors = FALSE))) 
corpus <- tm_map(corpus, tolower)
corpus <- tm_map(corpus, removePunctuation)
corpus <- tm_map(corpus, removeNumbers)
corpus <- tm_map(corpus, stripWhitespace)
corpus <- tm_map(corpus, PlainTextDocument)
corpus <- tm_map(corpus, removeWords, stopwords("english"))
corpus <- tm_map(corpus, removeWords, "na")

corpus

term.doc.matrix <- TermDocumentMatrix(corpus)
term.doc.matrix <- as.matrix(term.doc.matrix)
word.freqs <- sort(rowSums(term.doc.matrix), decreasing=TRUE) 
dm <- data.frame(word=names(word.freqs), freq=word.freqs)

wordcloud(dm$word, dm$freq, min.freq= 500, random.order=TRUE, rot.per=.25)

bigram.test <- NGramTokenizer(corpus, Weka_control(min = 2, max = 2)) 
bigram.test
bigram.df.test <- data.frame(table(bigram.test))
bigram.df.test <- bigram.df.test[order(bigram.df.test$Freq, decreasing = TRUE),]
bigram.df.test

bigram.df.test
filter(bigram.df.test, bigram.test == "still strubbling")

filter(trigram.df, trigram == "romantic date grocery")
bigram.df

bigram.df


```

